Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33 (580.03)  &  516.42 (502.60) & 679.67 (566.99) & 613.98 (491.47)  \\ \midrule
Median & 49.38 (47.5)   & 53.00 (54.5)  & 69.25 (42.72)             & 56.93 (40)\\ \midrule
Variance & 1223.08 (1236.94)  &  1148.11 (1149.09)  & 1352.37 (1229.4) & 1294.87  (1143.02) \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}

>>>>

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 580.0 (584.3)   &  502.6 (516.4)  & 567.0 (679.7)  & 491.5 (614.0)   \\ \midrule
Median & 47.5 (49.4)    & 54.5 (53.0) & 42.7 (69.3)  & 40.0 (56.9)\\ \midrule
Variance & 1237.0 (1223.1)  &  1149.1 (1148.1) & 1229.4 (1352.4) &  1143.0 (1294.9) \\ \midrule
Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}
